Climate-driven phytoplankton community variability in the Cariaco Basin, Venezuela

### 2025-06-29 agujournaltemplate.tex
pre-figure edit

\section{Materials and Methods}
% Here is text on Materials and Methods.
%
\subsection{Study Site}
    %Talk about the Basin shortly, then about the time series
    The Cariaco Ocean Time Series Program was established to explore the relationship between ocean surface processes and the sinking flux of particulate carbon. The Cariaco Basin (Figure~\ref{fig:map}) is a large (approximately 160 km long and 70 km wide) and deep (approximately 1,400 m) basin, situated on the northeastern Venezuelan continental shelf, with a sill to the north, running almost parallel to the coastline, at a mean depth of around \qty{100}{m}. This area is relatively productive ($\sim$ \qty{400}{g.C.m^{-2}.y^{-1}}), with primary production and vertical particulate organic matter fluxes exceeding those observed at BATS and HOT sites, resulting in the formation of anoxic conditions below \qty{\sim 275}{m} depth.

>>>>

\section{Materials and Methods}
% Here is text on Materials and Methods.
%
\subsection{Study Site}
    %Talk about the Basin shortly, then about the time series
    The Cariaco Ocean Time Series Program was established to explore the relationship between ocean surface processes and the sinking flux of particulate carbon. The Cariaco Basin (Figure~\ref{fig:map}) is a large (approximately 160 km long and 70 km wide) and deep (approximately 1,400 m) basin, situated on the northeastern Venezuelan continental shelf, with a sill to the north, running almost parallel to the coastline at a mean depth of around \qty{100}{m}. This area is relatively productive ($\sim$ \qty{400}{g.C.m^{-2}.y^{-1}}), with primary production and vertical particulate organic matter fluxes exceeding those observed at BATS and HOT sites, resulting in the formation of anoxic conditions below \qty{\sim 275}{m} depth.
